\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-07-03 paper.tex
Update on Overleaf.

This architecture moves away from classical layered approaches found in
robotics~\cite{Gat1998three, Volpe2001CLARAty, Goldberg2002}. Contrary to
layered architectures, interactions between components at the deliberative level
are here essentially bidirectional and we do not introduce layers of abstraction
amongst these deliberative components\footnote{We do have lower-level modules to
execute actions or manage sensors, but all cognition-related modules live in the
same global deliberative space.}. The natural language processing component
illustrates this structure: instead of being an independent input modality whose
outputs would be unidirectionally fed to ``higher'' decisional components, it
lives in the deliberative space at the same level as other deliberative
components, and uses the knowledge base in a bidirectional manner, to interpret,
disambiguate natural language, and eventually store newly produced
interpretations (natural language processing is discussed in
Section~\ref{sect|com}).

Our architecture however relates to \emph{Beliefs, Desires, Intentions} (BDI)
architectures. As put by Woolridge~\cite{Woolridge1999}, BDI architectures are
primarily focused on \emph{practical reasoning}, \ie the process of deciding,
step by step, which action to perform to reach a goal. The management of the
interaction between knowledge (the beliefs) and task and plan representation and
execution (the desires and the intentions) is central, and aims at selecting at
each step the best sub-goal. It becomes then an intention that the robot commits
to.

>>>>

Our architecture has not been designed to replicate or provide a
plausible model of human cognition.  The main design principles where
to nurture the decisional components of the robot with models of human
behaviour and human preferences in order to develop a pertinent
cognition for a robot that is able to serve and interact fluently with
humans. In this sense, it aims at the same objectives as\cite{Fong2005,trafton2013act}.

This architecture is based on the same principles as a number of known robotic
layered architectures~\cite{Alami98,Gat1998three,Volpe2001CLARAty, Goldberg2002}.

However, the main point for us was to refine and study in detail the
``internal'' architecture of the deliberative level.
The interactions between components at the deliberative level
are essentially bidirectional and we do not introduce layers of abstraction
amongst these deliberative components\footnote{We do have lower-level modules to
execute actions or manage sensors, but all cognition-related modules live in the
same global deliberative space.}. The natural language processing component
illustrates this structure: instead of being an independent input modality whose
outputs would be unidirectionally fed to ``higher'' decisional components, it
lives in the deliberative space at the same level as other deliberative
components, and uses the knowledge base in a bidirectional manner, to interpret,
disambiguate natural language, and eventually store newly produced
interpretations (natural language processing is discussed in
Section~\ref{sect|com}). 
Another example is the intricate relation between high-level symbolic
planning and geometric planning to deal with affordances and human preferences.

Our architecture relates to \emph{Beliefs, Desires, Intentions} (BDI)
architectures. As put by Woolridge~\cite{Woolridge1999}, BDI architectures are
primarily focused on \emph{practical reasoning}, \ie the process of deciding,
step by step, which action to perform to reach a goal. The management of the
interaction between knowledge (the beliefs) and task and plan representation and
execution (the desires and the intentions) is central, and aims at selecting at
each step the best sub-goal. It becomes then an intention that the robot commits
to.
